A practical guide for selecting the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate

### 2016-07-27 Main.Rmd
引用スタイルとbibtexの修正

---
title: "A practical guide for selecting the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate"
author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
bibliography: ~/Dropbox/R/List.bib
csl: ECB.csl
output:
  html_document:
    toc: true
    # toc_float: true
    depth: 3
    theme: sandstone
    self_contained: TRUE
    fig_caption: true
    pandoc_args: [
    "--latexmathml"
    ]
  # word_document:
  #   pandoc_args: [
  #   "--latexmathml"
  #   ]
---

>>>>

---
title: "A practical guide for selecting the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate"
author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
bibliography: ~/GitHub/BeeLabR/BibTex/with.bib
csl: ECB.csl
output:
  html_document:
    toc: TRUE
    depth: 3
    theme: sandstone
    self_contained: TRUE
    fig_caption: TRUE
    pandoc_args: [
    "--latexmathml"
    ]
  # word_document:
  #   pandoc_args: [
  #   "--latexmathml"
  #   ]
---
